Sampling-Based Motion Planning for Tracking Evolution of Dynamic Tunnels in Molecular Dynamics Simulations

### 2017-10-31 paper.tex
algorithm 6

\begin{algorithm}
%\setstretch{\straa}
{\small
\caption{Tunnel detection in dynamic protein
\label{alg::dynamic}
}
\KwIn{
    starting point $\qinit \in \CF$ in the first frame
}
\KwOut{list of configuration trees $\T_i$\;
}
\hrule
$\T_0$.add($\qinit)$\;
$P = \emptyset$; // list of all exit points \\
$G = $ empty graph\;
\For{$i  = 1 : n$}{
    $(\T_i, \SB)$ = treeTransfer($T_{i-1}, \CF^i$); // Alg.~\ref{alg::transfer}\\
    $(\T_i, P')$ = voidSpaceDetection($\T_{i},\SB)$; //Alg.~\ref{alg::main}\\
    $(V,E) =$ voidSpaceMerging($\T_{i}$); // V,E is a graph of merged void space 
    $C$ = find components in the graph (V,E)\;
    add components $C$ to graph $G$
    connect exit points $P'$ with their components in $G$\;
    connect active site $\qinit^i$ with its component in $G$\;
}
}
\end{algorithm}

>>>>

\begin{algorithm}
%\setstretch{\straa}
{\small
\caption{Tunnel detection in dynamic protein
\label{alg::dynamic}
}
\KwIn{
    starting point $\qinit \in \CF$ in the first frame
}
\KwOut{list of configuration trees $\T_i$, list of exit points $P$, graph of components $G$
}
\hrule
$\T_0$.add($\qinit)$\;
$P = \emptyset$; // list of all exit points \\
$G = $ empty graph\;
\For{$i  = 1 : n$}{
    $(\T_i, \SB)$ = treeTransfer($T_{i-1}, \CF^i$); // Alg.~\ref{alg::transfer}\\
    $(\T_i, P')$ = voidSpaceDetection($\T_{i},\SB)$; //Alg.~\ref{alg::main}\\
    $P = P \cup P'$\;
    $(V,E) =$ voidSpaceMerging($\T_{i}$); // V,E is a graph of merged void space  \\
    $C$ = find components in the graph (V,E)\; 
    add components $C$ to graph $G$ as nodes\;
    connect exit points $P'$ with their components (nodes) in $G$\;
    connect active site $\qinit \in \CF^i$ with its component (node) in $G$\;
}
}
\end{algorithm}
